Disease Knowledge Transfer across Neurodegenerative Diseases

### 2019-07-12 paper/paper.tex
added copyright form for miccai, re-orgnanised some files

%\newcommand{\expFld}{../resfiles/tad-drcTiny_JMD}
\newcommand{\expFld}{.}

@@

\begin{figure}[h]
 \centering
 \includegraphics[width=0.8\textwidth,trim=0 0 0 0,clip]{disease_knowledge_transfer_symbols.pdf}
 \caption{Diagram of the proposed DKT framework. We assume that each disease can be modelled as the evolution of abstract dysfunction scores (Y-axis, top row), each one related to different brain regions. Each region-specific dysfunction score then further models (X-axis, bottom row) the progression of several multimodal biomarkers within that same region. For instance, the temporal dysfunction, modelled as a biomarker in the disease specific model (top row), is the X-axis in the disease agnostic model (temporal unit, bottom row), which aggregates together abnormality from amyloid, tau and MR imaging within the temporal lobe. The biomarker relationships within the bottom units are assumed to be disease agnostic and shared across all diseases modelled. Knowledge transfer between the two diseases can then be achieved via the disease-agnostic units. Mathematical notation from section \ref{sec:method} is shown in red to ease understanding.}
 \label{fig:diagram}
\end{figure}

@@

%  \begin{table}
% \fontsize{6}{8}\selectfont
%  \centering
%  \begin{tabular}{c | c}
% & \textbf{Trajectory parameters} \\
% %\hline
%  Biomarker allocation &  $l_0:\{k_0, k_2, k_4\}$, $l_1: \{k_1, k_3, k_5\}$ \\
% Agnostic unit $l_0$ &  $\theta_0 = (1,5,0.2,0)$, $\theta_2 = (1,5,0.55,0)$,  $\theta_4 = (1,5,0.9,0)$  \\
% Agnostic unit $l_1$ & $\theta_1 = (1,10,0.2,0)$, $\theta_3 = (1,10,0.55,0)$, $\theta_5 = (1,10,0.9,0)$ \\
%   
% "Synthetic AD" & $\lambda_0^0 = (1, 0.3, -4, 0)$  and $\lambda_0^1 = (1, 0.2, 6, 0)$ \\
%  "Synthetic PCA" & $\lambda_1^0 = (1, 0.3, 6, 0)$ and $\lambda_1^1 = (1, 0.2, -4, 0)$ \\
% \hline
% & \textbf{Subject parameters} \\
%  Number of subjects & 100 (synthetic AD) and 50 (synthetic PCA) \\ 
%  Time-shifts $\beta_i$ & $\beta_i \sim U(-13,10)$ years \\
%  Diagnosis & $p(control) \propto Exp (-4.5)$,  $p(patient) \propto Exp (4.5)$\\
%  Data generation & 4 visits/subject, 1 year apart, $\epsilon_k = 0.05$\\ 
% \end{tabular}
% \caption{Parameters used for synthetic data generation, emulating the TADPOLE cohort and our own dataset.}
% \label{tab:synParams}
% \end{table}

@@

\begin{figure}[htp]
%\includegraphics[width=\textwidth]{../resfiles/synth/synth1_JMD/compTrueParams101_synth1_JMD.pdf}
\includegraphics[width=0.8\textwidth]{../resfiles/synth/synth1_JMD/compTrueParams105_synth1_JMD.pdf}
\begin{flushright}
\vspace{-16.0em}
\fontsize{5}{8.0}\selectfont
 \begin{tabular}{c}
% & \textbf{Trajectory parameters} \\
%\hline
 Biomarker allocation:\\
 $l_0:\{k_0, k_2, k_4\}$ \\
 $l_1: \{k_1, k_3, k_5\}$ \\
\hline
Agnostic unit $l_0$:\\
$\theta_0 = (1,5,0.20,0)$\\
$\theta_2 = (1,5,0.55,0)$\\
$\theta_4 = (1,5,0.90,0)$ \\
\hline
Agnostic unit $l_1$:\\
$\theta_1 = (1,10,0.20,0)$\\
$\theta_3 = (1,10,0.55,0)$\\
$\theta_5 = (1,10,0.90,0)$ \\
\hline  
Synthetic AD:\\
$\lambda_0^0 = (1, 0.3, -4, 0)$\\
$\lambda_0^1 = (1, 0.2,\ \ 6, 0)$ \\
\hline
Synthetic PCA:\\ 
$\lambda_1^0 = (1, 0.3,\ \ 6, 0)$\\
$\lambda_1^1 = (1, 0.2, -4, 0)$\\
% \hline
% & \textbf{Subject parameters} \\
%  Number of subjects & 100 (synthetic AD) and 50 (synthetic PCA) \\ 
%  Time-shifts $\beta_i$ & $\beta_i \sim U(-13,10)$ years \\
%  Diagnosis & $p(control) \propto Exp (-4.5)$,  $p(patient) \propto Exp (4.5)$\\
%  Data generation & 4 visits/subject, 1 year apart, $\epsilon_k = 0.05$\\ 
\end{tabular}
\end{flushright}
\vspace{-1em}
\caption[DKT Simulation Results - Comparison between true and DKT-estimated biomarker trajectories and subject time-shifts.]{Comparison between true and DKT-estimated subject time-shifts and biomarker trajectories. (top-left/top-middle) Scatter plots of the true shifts (y-axis) against estimated shifts (x-axis), for the 'synthetic AD' and 'synthetic PCA' diseases. We then show the DKT-estimated and true trajectories of the agnostic units within the 'synthetic AD' disease (top-right, "Dis0") and the 'synthetic PCA' disease (bottom-left, "Dis1"). Finally, we also show the biomarker trajectories within unit 0 (bottom-center) and unit 1 (bottom-right). Parameters used for generating the trajectory shapes are shown in the table on the right.}
  \label{fig:dktSynthTrajCompTrue}
\end{figure}

>>>>

%\newcommand{\expFld}{../resfiles/tad-drcTiny_JMD}
\newcommand{\expFld}{figures}

@@

\begin{figure}[h]
 \centering
 \includegraphics[width=0.8\textwidth,trim=0 0 0 0,clip]{figures/disease_knowledge_transfer_symbols.pdf}
 \caption{Diagram of the proposed DKT framework. We assume that each disease can be modelled as the evolution of abstract dysfunction scores (Y-axis, top row), each one related to different brain regions. Each region-specific dysfunction score then further models (X-axis, bottom row) the progression of several multimodal biomarkers within that same region. For instance, the temporal dysfunction, modelled as a biomarker in the disease specific model (top row), is the X-axis in the disease agnostic model (temporal unit, bottom row), which aggregates together abnormality from amyloid, tau and MR imaging within the temporal lobe. The biomarker relationships within the bottom units are assumed to be disease agnostic and shared across all diseases modelled. Knowledge transfer between the two diseases can then be achieved via the disease-agnostic units. Mathematical notation from section \ref{sec:method} is shown in red to ease understanding.}
 \label{fig:diagram}
\end{figure}

@@

@@

\begin{figure}[htp]
%\includegraphics[width=\textwidth]{../resfiles/synth/synth1_JMD/compTrueParams101_synth1_JMD.pdf}
\includegraphics[width=0.8\textwidth]{figures/compTrueParams105_synth1_JMD.pdf}
\begin{flushright}
\vspace{-16.0em}
\fontsize{5}{8.0}\selectfont
 \begin{tabular}{c}
% & \textbf{Trajectory parameters} \\
%\hline
 Biomarker allocation:\\
 $l_0:\{k_0, k_2, k_4\}$ \\
 $l_1: \{k_1, k_3, k_5\}$ \\
\hline
Agnostic unit $l_0$:\\
$\theta_0 = (1,5,0.20,0)$\\
$\theta_2 = (1,5,0.55,0)$\\
$\theta_4 = (1,5,0.90,0)$ \\
\hline
Agnostic unit $l_1$:\\
$\theta_1 = (1,10,0.20,0)$\\
$\theta_3 = (1,10,0.55,0)$\\
$\theta_5 = (1,10,0.90,0)$ \\
\hline  
Synthetic AD:\\
$\lambda_0^0 = (1, 0.3, -4, 0)$\\
$\lambda_0^1 = (1, 0.2,\ \ 6, 0)$ \\
\hline
Synthetic PCA:\\ 
$\lambda_1^0 = (1, 0.3,\ \ 6, 0)$\\
$\lambda_1^1 = (1, 0.2, -4, 0)$\\
% \hline
% & \textbf{Subject parameters} \\
%  Number of subjects & 100 (synthetic AD) and 50 (synthetic PCA) \\ 
%  Time-shifts $\beta_i$ & $\beta_i \sim U(-13,10)$ years \\
%  Diagnosis & $p(control) \propto Exp (-4.5)$,  $p(patient) \propto Exp (4.5)$\\
%  Data generation & 4 visits/subject, 1 year apart, $\epsilon_k = 0.05$\\ 
\end{tabular}
\end{flushright}
\vspace{-1em}
\caption[DKT Simulation Results - Comparison between true and DKT-estimated biomarker trajectories and subject time-shifts.]{Comparison between true and DKT-estimated subject time-shifts and biomarker trajectories. (top-left/top-middle) Scatter plots of the true shifts (y-axis) against estimated shifts (x-axis), for the 'synthetic AD' and 'synthetic PCA' diseases. We then show the DKT-estimated and true trajectories of the agnostic units within the 'synthetic AD' disease (top-right, "Dis0") and the 'synthetic PCA' disease (bottom-left, "Dis1"). Finally, we also show the biomarker trajectories within unit 0 (bottom-center) and unit 1 (bottom-right). Parameters used for generating the trajectory shapes are shown in the table on the right.}
  \label{fig:dktSynthTrajCompTrue}
\end{figure}
